Very simplified likelihood

### 2024-02-25 inst/very_simplified_likelihood.Rmd
logistic regression

```{r calculatelikes1,cache=F}
a <- seq(from=0.005,to=0.75,by=0.01)
La <- f_vec_arn(a,r=results$place[1]-1,results$runners[1]-1,log=TRUE)
La <- La - max(La,na.rm=TRUE)
plot(a,La,type='b',ylab='fishy')
abline(h=c(0,-2))
```

@@

>>>>

```{r calculatelikes1,cache=F}
a <- seq(from=0.005,to=0.85,by=0.01)
La <- f_vec_arn(a,r=results$place[1]-1,results$runners[1]-1,log=TRUE)
La <- La - max(La,na.rm=TRUE)
plot(a,La,type='b',ylab='fishy')
abline(h=c(0,-2))
```

@@

Above shows that there is no evidence to suggest that the Stirling
strength differs from the Auckland strength.  Now let's try a
logistic-style regression:

```{r logisticsupportparkrun,cache=FALSE}
results <- read.table("parkrun_results.txt",header=TRUE)
results
supp_logistic <- function(vec){
  alpha <- vec[1]
  beta <- vec[2]
  out <- 0
  for(i in seq_len(nrow(results))){
     LO <- alpha + beta*i
     strength <- exp(LO)/(1+exp(LO))
     out <- out + f_vec_arn(strength,results$place[i]-1,results$runners[i]-1,log=TRUE)
  }
  return(out+13400)
}

c(
supp_logistic(c(0,0)),
supp_logistic(c(0,0.01)),
supp_logistic(c(0,-0.01))
)

```{r optimlogist, cache=FALSE}
optim(par=c(0,0),fn=supp_logistic,control=list(fnscale=-1))
optim(par=c(0,0),fn=function(v){supp_logistic(vec=c(v[1],0))},control=list(fnscale=-1))
```
